\documentclass[11pt,a4paper]{article}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{amsthm}
\usepackage[margin=2.5cm]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}

\newcommand{\Spec}{\mathrm{Spec}}
\newcommand{\Zp}{\mathbb{Z}[1/p]}
\newcommand{\Sh}{\mathrm{Sh}}

\begin{document}

\title{Beyond Kardashev:\\
  The Arithmetic Civilization Scale and the\\
  Euler Product Console for Spacetime Engineering}

\author{Wright Brothers\\{\small Independent Research}}
\date{April 2026}
\maketitle

\begin{abstract}
Topos quantum theory (D\"oring-Isham) established that physical
propositions --- including energy conditions --- have truth values
that depend on the \emph{logical context} (topos) in which they are
evaluated. We showed in companion papers that the localization
$\mathbb{Z} \to \Zp$ changes the \'etale topos of $\Spec(\mathbb{Z})$,
allowing the weak energy condition to transition from ``true'' to
``false'' --- the first mechanism by which ``rewriting physical law''
becomes a coherent theoretical operation rather than a metaphor.

Building on this foundation, we propose the \emph{Euler product
console}: a device that independently controls $N$ prime channels
in the vacuum, generating $2^N$ programmable vacuum states, each
with distinct physical law. We analyze five applications
(programmable warp, selective matter transparency, the $\Spec(\mathbb{Z})$
computer, superluminal communication, and programmable chemistry),
define the \emph{arithmetic civilization scale} (A-0 through A-3)
that measures a civilization's ability to control physical law rather
than energy, and investigate five foundational questions:
the computational complexity of the $\Spec(\mathbb{Z})$ computer,
compatibility with causality via topos logic, the mathematical
structure of Type~A-3 civilizations (connections to the Langlands
program), energy requirements (showing A-2 may be achievable at
Kardashev Type~I), and ethical implications.
\end{abstract}

% ============================================================================
\section{Introduction: Why topos theory changes everything}
\label{sec:intro}
% ============================================================================

\subsection{The old barrier: physical law as immutable}

Throughout the history of physics, a tacit assumption has
prevailed: physical law is \emph{discovered}, never
\emph{modified}. We may harness electromagnetic forces, split
atoms, and accelerate particles, but the equations governing
these processes --- Maxwell's, Schr\"odinger's, Einstein's ---
are considered eternal and universal.

This assumption is not a theorem. It is a prejudice inherited
from the classical worldview, in which propositions about the
physical world are either true or false, absolutely and
context-independently.

\subsection{The topos revolution}

D\"oring and Isham~\cite{DoeringIsham2008} shattered this
assumption by reformulating quantum mechanics in topos-theoretic
language. In their framework:
\begin{itemize}
\item Physical propositions have truth values in a
  \emph{Heyting algebra}, not $\{0, 1\}$.
\item The truth value of a proposition depends on the
  \emph{context} --- the commutative subalgebra of observables
  chosen for measurement.
\item The same proposition can be ``true'' in one context and
  ``not true'' in another, without contradiction.
\end{itemize}

The Kochen-Specker theorem~\cite{KochenSpecker1967} had already
shown that quantum observables cannot have context-independent
values. D\"oring-Isham elevated this from a no-go result to a
\emph{constructive framework}: the topos $\Sh(\mathcal{V}(N))$
of presheaves over the context category provides a logically
consistent arena for quantum physics with context-dependent truth.

\subsection{From quantum context to arithmetic context}

In our companion papers~\cite{paper_A,paper_B}, we extended this
idea from quantum contexts to \emph{arithmetic contexts}.
The space $\Spec(\mathbb{Z})$ carries an \'etale topos
$\Sh(\Spec(\mathbb{Z})_{\mathrm{\acute{e}t}})$ with its own
internal logic. Localization $\mathbb{Z} \to \Zp$ induces a
morphism of topoi:
\begin{equation}
  \Sh(\Spec(\Zp)_{\mathrm{\acute{e}t}}) \to
  \Sh(\Spec(\mathbb{Z})_{\mathrm{\acute{e}t}}).
\end{equation}

The weak energy condition (WEC), interpreted as a proposition in
the arithmetic topos, has truth value ``true'' in
$\Sh(\Spec(\mathbb{Z})_{\mathrm{\acute{e}t}})$ and ``false'' in
$\Sh(\Spec(\Zp)_{\mathrm{\acute{e}t}})$~\cite{paper_B}.

This is the critical insight: \textbf{``rewriting physical law''
is not a metaphor but a topos morphism}. It is a mathematically
well-defined operation with computable consequences. The question
is no longer ``can physical law be changed?'' but ``how many
degrees of freedom does the change have, and what can we do
with them?''

% ============================================================================
\section{The Euler product console}
\label{sec:console}
% ============================================================================

\begin{definition}[Euler product console]
An $N$-channel Euler product console is a device that independently
controls the muting state (ON/OFF) of $N$ prime channels
$p_1, \ldots, p_N$ in a localized region of spacetime. The state
space is $\{0,1\}^N$, producing $2^N$ distinct vacuum
configurations, each with modified zeta function:
\begin{equation}
  \zeta_S(s) = \zeta(s) \prod_{p \in S} (1 - p^{-s}),
  \quad S \subseteq \{p_1, \ldots, p_N\}.
\end{equation}
\end{definition}

Each state $S$ corresponds to a vacuum with different physical
properties: different vacuum energy ($\zeta_S(-3)$), different
lepton $g-2$ corrections ($\zeta_S(-5)$, $\zeta_S(-9)$), and
different topological invariants ($K_1(\mathbb{Z}[S^{-1}])$).

The console is the spacetime analog of a computer's register file:
each prime is a bit, the Euler product is the instruction decoder,
and physical law is the output.

% ============================================================================
\section{The arithmetic civilization scale}
\label{sec:scale}
% ============================================================================

\begin{definition}[Arithmetic civilization scale]
\label{def:scale}
A civilization's level on the arithmetic scale is determined by
its ability to control the arithmetic structure of the vacuum:
\begin{description}
\item[Type A-0] \emph{Reads} physical law. Discovers but cannot
  modify the equations of nature. (Current humanity.)
\item[Type A-1] \emph{Locally modifies} physical law. Controls
  1--3 prime channels; achieves WEC violation and warp drive.
\item[Type A-2] \emph{Programs} physical law. Controls 10--100+
  prime channels; achieves selective matter transparency,
  programmable chemistry, and the $\Spec(\mathbb{Z})$ computer.
\item[Type A-3] \emph{Creates} new physical law. Operates on
  arithmetic structures beyond $\Spec(\mathbb{Z})$: number field
  extensions, function fields over finite fields, etc.
\end{description}
\end{definition}

The Kardashev scale~\cite{Kardashev1964} measures energy
\emph{quantity}. The arithmetic scale measures control over
physical law \emph{itself}. These are orthogonal axes: a
Kardashev Type~III civilization (galactic energy) may be
arithmetic Type~A-0 (unable to modify law), while an
arithmetic Type~A-2 civilization may require only Kardashev
Type~I energy (see Section~\ref{sec:energy}).

% ============================================================================
\section{Five foundational questions}
\label{sec:questions}
% ============================================================================

\subsection{Q1: Computational complexity of the $\Spec(\mathbb{Z})$ computer}

The $\Spec(\mathbb{Z})$ computer evaluates the Euler product
$\zeta_S(s)$ for any $S$ in $O(1)$ operations: set the channels
and measure the vacuum. Classically, computing
$\prod_{p \in S} (1-p^{-s})$ requires $O(|S|)$ multiplications
--- efficient, but not fundamentally different.

The true power emerges in \emph{search problems}. Consider:

\textbf{Problem.} Given a target value $\tau$, find
$S \subseteq \{p_1, \ldots, p_N\}$ such that
$|\zeta_S(-3) - \tau| < \epsilon$.

Classically: exhaustive search over $2^N$ subsets, $O(2^N)$.
Quantum (Grover): $O(2^{N/2})$.
$\Spec(\mathbb{Z})$ computer: if the vacuum \emph{relaxes} to the
state minimizing $|\zeta_S(-3) - \tau|$ (analogous to simulated
annealing), the solution is found in the relaxation time
$\tau_{\mathrm{relax}}$, which may be polynomial in $N$.

More profoundly: the zeros of $\zeta(s)$ are encoded in the vacuum
spectrum. A $\Spec(\mathbb{Z})$ computer could, in principle,
\emph{measure} the location of Riemann zeros as physical observables.

\begin{conjecture}[Physical Riemann hypothesis test]
\label{conj:riemann}
A sufficiently powerful $\Spec(\mathbb{Z})$ computer can determine
whether all nontrivial zeros of $\zeta(s)$ lie on
$\mathrm{Re}(s) = 1/2$ by measuring the vacuum spectral density.
\end{conjecture}

This would transform the Riemann hypothesis from pure mathematics
into experimental science.

\subsection{Q2: Causality and topos logic}

Superluminal communication via the console's wall radiation
raises the standard objection: closed timelike curves and
causality violation.

The topos-theoretic resolution: causality is a proposition
evaluated within a specific topos. In
$\Sh(\Spec(\mathbb{Z})_{\mathrm{\acute{e}t}})$, the causal
structure is the standard Lorentzian one. In
$\Sh(\Spec(\Zp)_{\mathrm{\acute{e}t}})$, the causal structure
may differ.

Malament's theorem~\cite{Malament1977} states that the causal
structure determines the spacetime topology (up to conformal
factor). In our framework, different topoi define different
causal structures, and hence different spacetime topologies.
Communication through a $\Spec(\Zp)$ region uses a
\emph{different causal structure} --- it does not ``violate''
the original causality but operates in a domain where
causality has a different logical form.

This is analogous to quantum teleportation: it does not violate
no-signaling (a ``causal'' constraint) because the protocol
requires a classical channel. Similarly, console-mediated
communication may require an ``arithmetic channel'' (the console
state) that prevents genuine paradoxes.

A rigorous treatment requires formulating Malament's theorem
within the topos $\Sh(\Spec(\mathbb{Z})_{\mathrm{\acute{e}t}})$
and showing that the morphism to $\Sh(\Spec(\Zp)_{\mathrm{\acute{e}t}})$
preserves a suitable generalization of causal order. This is an
open problem.

\subsection{Q3: Type A-3 and the Langlands program}

Type~A-3 civilizations operate on arithmetic structures beyond
$\Spec(\mathbb{Z})$. The natural mathematical framework is
the Langlands program~\cite{Langlands1970,Frenkel2007}, which
connects:
\begin{itemize}
\item Automorphic forms on reductive groups $G$ over number fields,
\item Galois representations $\mathrm{Gal}(\bar{\mathbb{Q}}/\mathbb{Q}) \to {}^LG$,
\item $L$-functions generalizing $\zeta(s)$.
\end{itemize}

If our universe corresponds to $\Spec(\mathbb{Z})$ with its
$L$-function $\zeta(s)$, then:
\begin{itemize}
\item A universe over $\Spec(\mathcal{O}_K)$ (ring of integers
  of a number field $K$) would have Dedekind zeta function
  $\zeta_K(s)$ as its vacuum structure.
\item The class number $h_K$ measures the failure of unique
  factorization in $\mathcal{O}_K$. Physically: $h_K > 1$
  means the Euler product is ``incomplete'' --- some primes
  split into multiple factors, creating \emph{redundant}
  vacuum channels.
\item The Galois group $\mathrm{Gal}(K/\mathbb{Q})$ acts as
  a symmetry group of the new vacuum, distinct from the
  Bost-Connes Galois symmetry.
\end{itemize}

\begin{conjecture}[Langlands-physics correspondence]
Type~A-3 spacetime engineering corresponds to the arithmetic
side of the Langlands program: each automorphic representation
defines a possible vacuum structure, and the Langlands functoriality
corresponds to ``translation'' between different vacua.
\end{conjecture}

Specific examples:
$\Spec(\mathbb{Z}[i])$ (Gaussian integers): the prime $2$ splits
as $2 = -i(1+i)^2$, creating a new prime $(1+i)$ with no analog
in $\Spec(\mathbb{Z})$. Physically: a new fundamental interaction
that does not exist in our universe.

$\Spec(\mathbb{Z}[\sqrt{-5}])$: class number $h = 2$.
Unique factorization fails: $6 = 2 \times 3 = (1+\sqrt{-5})(1-\sqrt{-5})$.
Physically: the ``same'' process can occur via two inequivalent
channels, introducing a fundamental non-determinism beyond
quantum mechanics.

\subsection{Q4: Energy requirements}
\label{sec:energy}

The energy to maintain an arithmetic vacuum modification is
\emph{not} proportional to the strength of the modification.
As shown in the companion paper on safety~\cite{paper_J},
the modification is topological (a $K_1$ change), not energetic.

The energy required is:
\begin{enumerate}
\item \textbf{Initial creation:} the energy to establish the domain
  wall $V(p) = \Spec(\mathbb{F}_p)$. This is the wall surface
  energy $E_{\mathrm{wall}} = 4\pi R^2 \sigma$, where
  $\sigma \sim \hbar\omega_0 / \delta^2$ and
  $\delta \sim \lP \log p$ is the wall thickness.
  For a 1\,m bubble: $E_{\mathrm{wall}} \sim 10^{10}\,\mathrm{J}$
  (comparable to a lightning bolt).
\item \textbf{Maintenance:} compensating the wall radiation
  $P_{\mathrm{rad}} = \sigma_{\mathrm{SB}} T_{\mathrm{wall}}^4 \times 4\pi R^2$.
  For $T_{\mathrm{wall}} \sim 30\,\mathrm{mK}$ and $R = 1\,\mathrm{m}$:
  $P_{\mathrm{rad}} \sim 10^{-13}\,\mathrm{W}$ --- essentially zero.
\item \textbf{Multi-channel operation:} each additional channel adds
  $O(E_{\mathrm{wall}})$ to the creation cost but negligible
  maintenance. An $N = 20$ channel console:
  $E_{\mathrm{total}} \sim 20 \times 10^{10} \sim 10^{12}\,\mathrm{J}$
  $\approx 0.3\,\mathrm{GWh}$ --- achievable with a small power plant.
\end{enumerate}

\begin{proposition}
A Type~A-2 civilization (20-channel Euler product console) requires
$\sim 10^{12}\,\mathrm{J}$ of energy, well within the capacity of
a Kardashev Type~I civilization ($\sim 10^{16}\,\mathrm{W}$).
\end{proposition}

This confirms the orthogonality of the Kardashev and arithmetic
scales: mastering physical law requires intelligence and
technology, not brute energy.

\subsection{Q5: Ethics of physical law modification}

A civilization capable of modifying physical law faces
unprecedented ethical questions:
\begin{itemize}
\item \textbf{Consent:} Modifying the vacuum in a region affects
  all matter within it. Do the inhabitants consent?
\item \textbf{Reversibility:} The parity law (Section~5 of~\cite{paper_J})
  guarantees reversibility --- but only if the ``undo'' operation
  is performed. Who holds the kill switch?
\item \textbf{Asymmetry:} A Type~A-2 civilization interacting with
  a Type~A-0 civilization has an insurmountable advantage ---
  not in weapons or resources, but in the \emph{rules of physics}
  governing the interaction.
\item \textbf{Cosmic responsibility:} If other regions of the
  universe host intelligence, modifying physical law near them
  (even locally) could affect their existence.
\end{itemize}

We propose that a Type~A-1+ civilization should adopt an
\emph{arithmetic prime directive}: no modification of physical
law in regions containing or potentially containing conscious
observers, without their informed consent.

% ============================================================================
\section{Conclusion}
% ============================================================================

The D\"oring-Isham topos framework transformed ``rewriting
physical law'' from metaphor to mathematics. Localization on
$\Spec(\mathbb{Z})$ is a concrete instance: a topos morphism
that changes the truth value of the WEC. The Euler product
console extends this to $N$-channel programmability with
$2^N$ vacuum states.

The arithmetic civilization scale measures what Kardashev
cannot: control over physical law itself. Our analysis shows
that Type~A-2 (programmable physical law via a 20-channel console)
requires only $\sim 10^{12}\,\mathrm{J}$ --- achievable with
current energy technology, awaiting only the realization of
arithmetic vacuum engineering.

The deepest implication is Type~A-3: civilizations that
operate on number field extensions of $\Spec(\mathbb{Z})$,
connecting to the Langlands program and potentially creating
physical interactions with no analog in our universe.

The path from A-0 to A-1 begins with the SQUID experiment
proposed in~\cite{paper_A}. If it succeeds, the question
``can physical law be modified?'' will have an experimental
answer, and the journey toward programmable physics will begin.

\begin{thebibliography}{20}
\bibitem{DoeringIsham2008} A.~D\"oring and C.~J.~Isham, J. Math. Phys. \textbf{49}, 053515 (2008).
\bibitem{KochenSpecker1967} S.~Kochen and E.~P.~Specker, J. Math. Mech. \textbf{17}, 59 (1967).
\bibitem{paper_A} Wright Brothers, companion paper A (2026).
\bibitem{paper_B} Wright Brothers, companion paper B (2026).
\bibitem{paper_J} Wright Brothers, companion paper J (2026).
\bibitem{Kardashev1964} N.~S.~Kardashev, Sov. Astron. \textbf{8}, 217 (1964).
\bibitem{Malament1977} D.~Malament, J. Math. Phys. \textbf{18}, 1399 (1977).
\bibitem{Langlands1970} R.~P.~Langlands, \emph{Problems in the Theory of Automorphic Forms}, Springer LNM \textbf{170} (1970).
\bibitem{Frenkel2007} E.~Frenkel, Bull. Amer. Math. Soc. \textbf{44}, 451 (2007).
\end{thebibliography}

\end{document}
