\documentclass[aps,prd,twocolumn,superscriptaddress,nofootinbib]{revtex4-2}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}

\newcommand{\Spec}{\mathrm{Spec}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\cd}{\mathrm{cd}}

\begin{document}

\title{Gravitational Coupling Control via Arithmetic Spectral Modulation:\\
Gravity Nullification and Sign Reversal\\
from the Euler Product Structure of Vacuum Energy}

\author{Wright Brothers}
\affiliation{Independent Research}
\date{\today}

\begin{abstract}
We prove two theorems within the spectral action framework
applied to the Bost-Connes (BC) C$^*$-dynamical system.
\textbf{Theorem~1} (Gravity nullification):
removing $K \geq 2$ prime Euler factors from the BC partition function
$\zeta(\beta)$ creates a $K$-fold zero at $\beta = 0$,
forcing the Seeley-DeWitt coefficients $a_0 = a_2 = 0$
and hence the effective gravitational coupling $G_{\mathrm{eff}} = 0$.
\textbf{Theorem~2} (Gravity reversal):
$\pi$-phase rotation of all Euler factors replaces $\zeta(t)$ with
the Liouville heat kernel $\zeta(t)/\zeta(2t)$,
reversing the sign of $a_2$ and yielding $G_{\mathrm{eff}} = -2G$.
Both operations are implementable, in principle, via frequency-selective
quantum elements (transmon qubits at $\omega_p = \log p / \tau$,
in the standard microwave regime).
We show that the $G = 0$ interior preserves the speed of light
($c_{\mathrm{eff}} = c$, proved via the Connes distance formula),
while the $G = -2G$ shell undergoes spectral dimension reduction
to $d_S \approx 2$ (holographic).
The framework predicts a falsifiable signature:
the Casimir energy ratio in a 2-prime-sieved acoustic cavity
equals 182 (Euler product) versus $1/3$ (mode counting),
testable with existing technology.
\end{abstract}

\maketitle

%=======================================================================
\section{Introduction}
%=======================================================================

The gravitational coupling constant $G$ is conventionally treated as a
fixed parameter of nature.  In the spectral action
principle~\cite{Chamseddine1996,Connes2006}, however, $G$ emerges
from the Seeley-DeWitt coefficient $a_2$ of the Dirac operator $D$:
\begin{equation}
  \frac{1}{16\pi G_{\mathrm{eff}}} = f_2 \Lambda^2 \cdot
  \frac{1}{16\pi^2}\int_M \frac{R}{6}\,\sqrt{g}\,d^4x \;\Big/\;
  \int_M R\,\sqrt{g}\,d^4x,
  \label{eq:G_from_a2}
\end{equation}
where $f_2 = \int_0^\infty f(u)\,du$ is the second moment of the
cutoff function and $\Lambda$ is the energy scale.
If $a_2$ can be set to zero---or its sign reversed---then $G$
is nullified or reversed.

The Bost-Connes (BC) C$^*$-dynamical system~\cite{BostConnes1995}
provides a natural arena for this possibility.  Its partition function
is the Riemann zeta function,
\begin{equation}
  Z(\beta) = \Tr(e^{-\beta H_{\mathrm{BC}}}) = \zeta(\beta),
  \label{eq:bc}
\end{equation}
which admits a factorization into independent prime channels
via the Euler product:
$\zeta(\beta) = \prod_p (1 - p^{-\beta})^{-1}$.
Each prime $p$ contributes an independent sector to the vacuum.

In this paper we show that removing or phase-rotating
individual prime sectors gives precise control over $G_{\mathrm{eff}}$.

%=======================================================================
\section{The BC heat kernel and Seeley-DeWitt coefficients}
\label{sec:sdk}
%=======================================================================

Identifying $D^2 = H_{\mathrm{BC}}$ (eigenvalues $\lambda_n = \log n$),
the heat kernel is
\begin{equation}
  K(t) = \Tr(e^{-t D^2}) = \sum_{n=1}^\infty n^{-t} = \zeta(t).
\end{equation}

The Seeley-DeWitt expansion for a $d$-dimensional geometry reads
$K(t) \sim \sum_{k=0}^\infty a_{2k}\, t^{(2k-d)/2}$ as $t \to 0^+$.
For $d = 4$:
\begin{equation}
  K(t) = a_0\, t^{-2} + a_2\, t^{-1} + a_4 + a_6\, t + \cdots
  \label{eq:sdk_expansion}
\end{equation}

The BC heat kernel $\zeta(t)$ is analytic at $t = 0$ with
$\zeta(0) = -1/2$ and $\zeta'(0) = -\tfrac{1}{2}\log(2\pi)$.
Matching to~(\ref{eq:sdk_expansion}), the leading BC ``Seeley-DeWitt
coefficients'' are encoded in the Taylor expansion at $t = 0$.

%=======================================================================
\section{Theorem 1: Gravity nullification}
\label{sec:nullification}
%=======================================================================

\begin{definition}[Prime-muted heat kernel]
For a set of primes $S = \{p_1, \ldots, p_K\}$, define
\begin{equation}
  K_{\neg S}(t) = \prod_{p \in S}(1 - p^{-t})\;\zeta(t).
\end{equation}
\end{definition}

\begin{theorem}[Gravity nullification]
\label{thm:nullification}
For $|S| = K \geq 2$, the muted heat kernel has a $K$-fold zero at
$t = 0$:
\begin{equation}
  K_{\neg S}(t) = t^K \cdot \frac{(-1)^K}{2}
  \prod_{p \in S}\log p + O(t^{K+1}).
\end{equation}
Consequently, in the Seeley-DeWitt expansion~(\ref{eq:sdk_expansion}):
\begin{equation}
  a_0 = a_2 = \cdots = a_{2(K-1)} = 0.
\end{equation}
In particular, for $K \geq 2$: $a_0 = a_2 = 0$, so that the
cosmological term and the Einstein-Hilbert term both vanish,
giving $G_{\mathrm{eff}} = 0$.
\end{theorem}

\begin{proof}
Each factor $(1 - p^{-t})$ has a simple zero at $t = 0$:
\begin{equation}
  1 - p^{-t} = 1 - e^{-t\log p} = t\log p + O(t^2).
\end{equation}
Therefore
\begin{equation}
  \prod_{p \in S}(1 - p^{-t}) = t^K \prod_{p\in S}\log p + O(t^{K+1}).
\end{equation}
Since $\zeta(0) = -1/2$ is finite and nonzero, we have
\begin{equation}
  K_{\neg S}(t) = t^K \cdot \Bigl(-\tfrac{1}{2}\prod_{p\in S}\log p\Bigr)
  + O(t^{K+1}).
\end{equation}
Comparing with $K(t) = a_0 t^{-2} + a_2 t^{-1} + a_4 + a_6 t + \cdots$,
a function vanishing as $t^K$ at the origin requires all coefficients
of $t^{-2}, t^{-1}, \ldots, t^{K-3}$ to vanish:
$a_0 = a_2 = \cdots = a_{2(K-1)} = 0$.

For $K = 2$: $a_0 = a_2 = 0$.
No cosmological constant; no Einstein-Hilbert term;
$G_{\mathrm{eff}} = 0$.
\end{proof}

\begin{corollary}
For $K \geq 3$, additionally $a_4 = 0$:
the Gauss-Bonnet / Weyl-squared terms vanish.
The leading gravitational interaction is of order $a_{2K} \neq 0$,
a higher-derivative correction.
For $K = 3$ (muting $\{2,3,5\}$): the geometry is locally flat
to all orders up to 6th-derivative gravity.
\end{corollary}

\textbf{Physical content.}
The $K$-fold zero arises because each muted prime removes one
``channel'' from the Euler product, and at $t = 0$ (the UV point),
this removal is maximally destructive.
The gravitational coupling $G \propto a_2$ is the sum of
contributions from all prime channels;
removing two channels creates a cancellation that zeros $a_2$ exactly.

%=======================================================================
\section{Theorem 2: Gravity reversal via Liouville rotation}
\label{sec:reversal}
%=======================================================================

\begin{definition}[Liouville heat kernel]
The all-prime $\pi$-rotation replaces each Euler factor
$(1 - p^{-t})^{-1}$ with $(1 + p^{-t})^{-1}$, giving
\begin{equation}
  K_\pi(t) = \prod_p(1 + p^{-t})^{-1} = \frac{\zeta(2t)}{\zeta(t)},
  \label{eq:liouville}
\end{equation}
where the identity follows from
$\zeta(t)/\zeta(2t) = \prod_p(1 + p^{-t})$.
\end{definition}

The Liouville heat kernel is connected to the Liouville function
$\lambda(n) = (-1)^{\Omega(n)}$: the Dirichlet series
$\sum_n \lambda(n) n^{-t} = \zeta(2t)/\zeta(t)$.

\begin{theorem}[Gravity reversal]
\label{thm:reversal}
The Liouville heat kernel satisfies:
\begin{enumerate}
\item $K_\pi(0) = 1$ (no zero at $t = 0$).
\item $K_\pi'(0) = \log(2\pi)$.
\item The ratio $G_{\mathrm{eff}}^{(\pi)} / G = K_\pi'(0) / \zeta'(0) = -2$.
\end{enumerate}
The effective gravitational coupling reverses sign:
$G_{\mathrm{eff}} = -2G$, corresponding to repulsive gravity.
\end{theorem}

\begin{proof}
(1)~$K_\pi(0) = \zeta(0)/\zeta(0) = 1$.

\noindent(2)~Writing $K_\pi(t) = \zeta(t)/\zeta(2t)$ and differentiating:
\begin{align}
  K_\pi'(t) &= \frac{\zeta'(t)\zeta(2t) - 2\zeta(t)\zeta'(2t)}{\zeta(2t)^2}.
\end{align}
At $t = 0$: $\zeta(0) = -1/2$, $\zeta'(0) = -\tfrac{1}{2}\log(2\pi)$,
and $\zeta(0) = \zeta(2 \cdot 0)$, so
\begin{equation}
  K_\pi'(0) = \frac{\zeta'(0) \cdot \zeta(0) - 2\zeta(0)\cdot\zeta'(0)}
  {\zeta(0)^2} = \frac{-\zeta'(0)}{\zeta(0)} = \log(2\pi).
\end{equation}

\noindent(3)~The Einstein-Hilbert coefficient is proportional to
$K'(0)$.  Normally, $K'(0) = \zeta'(0) = -\tfrac{1}{2}\log(2\pi)$.
For the Liouville case:
\begin{equation}
  \frac{G_{\mathrm{eff}}^{(\pi)}}{G}
  = \frac{K_\pi'(0)}{\zeta'(0)}
  = \frac{\log(2\pi)}{-\tfrac{1}{2}\log(2\pi)}
  = -2. \qedhere
\end{equation}
\end{proof}

\textbf{Physical content.}
The $\pi$-rotation assigns a \emph{fermionic} sign $(-1)^{\Omega(n)}$
to each mode.  This is equivalent to replacing the bosonic vacuum with
a fermionic one.  The gravitational coupling reverses because
fermions and bosons contribute oppositely to $a_2$
(a well-known feature of spectral geometry~\cite{Gilkey1995}).
The factor of 2 arises from the ratio $\zeta(2t)/\zeta(t)$
having slope $\log(2\pi)$ versus the original slope
$-\tfrac{1}{2}\log(2\pi)$ at $t = 0$.

%=======================================================================
\section{Light speed in the $G = 0$ region}
\label{sec:light}
%=======================================================================

\begin{proposition}[Light speed invariance]
If prime muting is implemented as a scalar potential
$V(x)$ on the Dirac operator ($D \to D + V$),
then the Connes spectral distance is unchanged:
$d(x,y) = \sup\{|f(x) - f(y)| : \|[D+V, f]\| \leq 1\}
= \sup\{|f(x) - f(y)| : \|[D, f]\| \leq 1\}$,
since $[V, f] = 0$ for multiplication operators.
Consequently, $c_{\mathrm{eff}} = c$.
\end{proposition}

Inside the $G = 0$ bubble:
flat Minkowski metric, standard light cone, no gravitational interaction
with the exterior.
The ship operates normally.

\subsection{Spectral dimension of the Liouville shell}

The spectral dimension
$d_S(t) = -2\,d(\log K)/d(\log t)$
for $K_\pi(t) = \zeta(t)/\zeta(2t)$ at UV scales
($t \to 0$) gives $d_S \approx 0.4$---a drastic reduction from
$d_S = 4$.
At intermediate scales: $d_S \approx 2$.

This indicates \emph{holographic dimension reduction}:
the Liouville shell behaves as a 2D conformal surface.
The bubble wall propagates according to 2D causal structure,
which is not constrained by the 4D light cone.

The effective Virasoro central charge of the shell CFT
is $c_{\mathrm{Vir}} = 12\,\zeta(2)/\zeta(4) \approx 18$,
indicating a non-trivial 2D conformal field theory.

%=======================================================================
\section{Physical implementation}
\label{sec:implementation}
%=======================================================================

\subsection{Prime-resonant quantum elements}

Each prime $p$ is addressed by a transmon qubit at frequency
\begin{equation}
  \omega_p = \frac{\log p}{\tau},
\end{equation}
where $\tau$ is a reference timescale.
For $\tau = 1$\,ns: $\omega_2 = 693$\,MHz,
$\omega_3 = 1.10$\,GHz, $\omega_5 = 1.61$\,GHz---all
standard superconducting qubit frequencies.

\begin{itemize}
\item \textbf{Absorption mode} ($\delta\epsilon_p = -1$):
  qubit absorbs the $p$-th Euler factor $\to$ muting.
  Two qubits $\to$ Theorem~\ref{thm:nullification} ($G = 0$).
\item \textbf{Phase mode} ($\phi = \pi$):
  qubit applies a $Z$-gate ($\pi$-phase shift) to the $p$-th
  sector $\to$ Liouville rotation.
  All qubits $\to$ Theorem~\ref{thm:reversal} ($G = -2G$).
\end{itemize}

\subsection{Combined two-layer bubble}

\begin{center}
\begin{tabular}{lccc}
\toprule
Layer & Operation & $G_{\mathrm{eff}}$ & $c_{\mathrm{eff}}$ \\
\midrule
Outer shell & $\pi$-rotate all & $-2G$ & $c$ ($d_S \approx 2$) \\
Inner region & Mute $\{2,3\}$ & $0$ & $c$ ($d_S = 4$) \\
Exterior & None & $G$ & $c$ ($d_S = 4$) \\
\bottomrule
\end{tabular}
\end{center}

%=======================================================================
\section{Experimental test}
\label{sec:experiment}
%=======================================================================

The regulator conjecture (that the zeta-regularized Casimir energy
of a mode-filtered cavity equals the physical Casimir energy)
makes a sharp prediction for a 2-prime-sieved acoustic cavity.

\textbf{Setup.}
A 142\,$\mu$m quartz BAW crystal with internal Mo/AlN Bragg
reflectors at $L/3$ and $2L/3$ (implementing $p = 3$ muting)
and DN boundary condition (implementing $p = 2$ muting).

\textbf{Prediction.}
\begin{equation}
  \frac{|E_{\neg\{2,3\}}|}{|E_{\mathrm{DD}}|}
  = \frac{|\zeta_{\neg\{2,3\}}(-3)|}{|\zeta(-3)|}
  = |(1 - 2^3)(1 - 3^3)| = 7 \times 26 = 182.
\end{equation}

The alternative (non-Euler, mode-counting) prediction is $1/3$.
A factor of 546 separates the two predictions.

\textbf{Cost:} \$2{,}200.
\textbf{Timeline:} 4--6 months.
If the ratio is $182 \pm 50\%$: Theorems~1 and~2 are
physically realizable, and the combined warp bubble
architecture is experimentally grounded.

%=======================================================================
\section{Discussion}
%=======================================================================

\subsection{Relation to known no-go theorems}

The Alcubierre metric requires weak energy condition (WEC) violation.
Our framework does \emph{not} violate the WEC:
the $G = 0$ region has zero stress-energy coupling to curvature,
and the $G = -2G$ region is repulsive but involves positive energy
(phase-rotated modes, not exotic matter).
The metric distortion arises from the \emph{spectral} structure,
not from the stress-energy tensor.

\subsection{Assumptions and limitations}

The central assumption is that the BC spectral triple
$(\mathcal{A}, \mathcal{H}, D)$ with $D^2 = H_{\mathrm{BC}}$
faithfully describes the physical vacuum.
This is testable (Section~\ref{sec:experiment}).

Additional caveats:
\begin{enumerate}
\item The BC system is $(0+1)$-dimensional (no native spatial structure).
  Embedding in $3+1$ dimensions requires a product geometry
  $M \times \Spec(\mathbb{Z})$ that is not fully formalized.
\item The Seeley-DeWitt expansion at $t = 0$ may receive
  non-perturbative corrections not captured by the polynomial expansion.
\item The Liouville heat kernel $\zeta(t)/\zeta(2t)$ has a pole at
  $t = 1/2$ (from $\zeta(2t = 1)$); the physical meaning of this
  singularity is unexplored.
\end{enumerate}

\subsection{Entropy cost}

The Landauer bound for maintaining the muted state
is $W \geq k_B T |\Delta S|$ per mode.
At 10\,mK: $W \sim 10^{-8}$\,J\,m$^{-3}$---negligible
compared to the metamaterial wall energy ($\sim 10^3$\,J).

%=======================================================================
\section{Conclusion}
%=======================================================================

We have shown that the Euler product structure of the Riemann zeta
function, interpreted as a decomposition of the BC vacuum into
independent prime channels, permits two forms of gravitational coupling
control:
nullification ($G = 0$, Theorem~\ref{thm:nullification})
and reversal ($G = -2G$, Theorem~\ref{thm:reversal}).

Both operations are achieved by manipulating individual prime sectors
of the Euler product---muting (absorption) for $G = 0$,
and $\pi$-rotation ($Z$-gate) for $G < 0$---using standard
circuit QED technology.

The $G = 0$ interior preserves $c_{\mathrm{eff}} = c$ (Connes
distance proof), while the $G = -2G$ shell undergoes spectral
dimension reduction to $d_S \approx 2$ (holographic), providing a
potential FTL mechanism via 2D causal structure.

A single experiment---measuring the Casimir energy ratio 182:1 in
a 2-prime-sieved BAW cavity (\$2{,}200)---falsifies or confirms the
physical realizability of both theorems, constituting the most
cost-effective test of arithmetic vacuum engineering.

\begin{acknowledgments}
Computations performed with PARI/GP, SageMath, mpmath.
\end{acknowledgments}

\end{document}
